---
title: "Linear Model from Web"
author: "Ever De Leon"
date: "Spring 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```
# Introduction

We will produce three equation models to get:  
1. sim score based on arm strength  
2. sim score based on grip strength  
3. sim score based on both arem and grip strength  

For each model, we will predict sim for arm=88, grip=94

# Methods 
We have numerical responses (sim score) and numerical explanatory variables (arm and grip strength)

## Model 1 SIM~ARM

### scatterplot
```{r}
plot(SIMS~ARM,data=data)
```

There is a positive relationship between SIMS and ARM. If this ws a perfect linear relationship, they would be on a straight line. In this case, they are not on a straight line, so the correlation maybe about 0.8.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

This summarizes the correlation between ARM strength and the SIMS score.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The P-value for the coefficient of ARM is 0.0000000000000002.

#### Predict at target point

```{r}
SIMSpredict=predict.lm(model.1,newdata=data.frame(ARM=88,GRIP=94), interval = "confidence")
print(SIMSpredict)
```

The prediction for ARM=88, GRIP=94 is .71

#### scatterplot with model fit

```{r}
plot(SIMS~ARM,data=data)
abline(model.1,col="red")
```

This is a scatter plot with a function on it, at ARM strength 88, the 95 percent confidence interval is between 0.49 and 0.92.

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

There is a positive relationship between SIMS and GRIP. If this ws a perfect linear relationship, they would be on a straight line. In this case, they are not on a straight line, so the correlation maybe about 0.8.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

This summarizes the correlation between GRIP strength and the SIMS score.

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  

The P-value for the coefficient of ARM is 0.0000000000000002.

#### predict model.2 at target point

```{r}
SIMSpredict=predict.lm(model.2,newdata=data.frame(ARM=88,GRIP=94), interval = "confidence")
print(SIMSpredict)
```

The prediction for ARM=88, GRIP=94 is -0.54

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
m = data.frame(data["GRIP"],data["ARM"],data["SIMS"])
cor(m)
```

The table shows that the SIMS correlates with GRIP in a positive manner (0.64) and SIMS correlates with ARM also in a positive manner (0.69). This says these variables are useful in predicting SIMS.

```{r}
plot(data$GRIP,data$ARM)
```

Plot shows GRIP and Arm are not independent, so this is not necessarily a good model.
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 = lm(SIMS~GRIP+ARM,data = data)
print(summary.lm(model.3))
newPoint = data.frame(GRIP=94,ARM=88)
predict.lm(model.3, newPoint, interval = 'prediction')
```

The 95% confidence interval is SIMS is between -2.13 and 2.43. Since this interval contains 0, we do not have a very good prediction for SIMS. 

#### predict model.3 at target point
  
```{r}
newPoint = data.frame(GRIP=94,ARM=88)
predict.lm(model.3, newPoint, interval = 'prediction')
```


## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```

p-value is 0.000004994 which is less than 0.05 so we can concluded that model.3 is better than model.1

### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```
p-value is 0.000000001495 which is less than 0.05, so we can concluded that model.2 is better than model.3.

## Informally compare model.1 with model.2

Since model.3 is better than model.1 and model.2 is better than model.3, then we can conclude that model.2 is better then model.1