---
title: "Linear Model from Web"
author: "Ever De Leon"
date: "Spring 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```
# Introduction

We will produce three equation models to get:  
1. sim score based on arm strength  
2. sim score based on grip strength  
3. sim score based on both arem and grip strength  

For each model, we will predict sim for arm=88, grip=94

# Methods 
We have numerical responses (sim score) and numerical explanatory variables (arm and grip strength)

## Model 1 SIM~ARMS

### scatterplot
```{r}
plot(SIMS~ARM,data=data)
```

There is a positive relationship between SIMS and ARM. If this ws a perfect linear relationship, they would be on a straight line. In this case, they are not on a straight line, so the correlation maybe about 0.8.

### Numerical results


### Inferential  (Build model.1)

#### Predict at target point


#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

